---
title: "Text analizes classs"
author: "Kristof Menyhert"
date: "2018-02-22"
output: html_document
---

## Coding example:

In this exercise I am presenting an example what can you do with the gutenbergR package combining with the tidytext and the tidyverse package. Then do some basic piloting with ggplot.

With the help of the tools mentioned above we can see how words in two books are related to each other. In this way we can have some insights how the two books are relate to each other, notice some important words for each book.

In the following lines you can find an example how to deal do this:

Load some packages:
```{r, warning=FALSE, message=FALSE}
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(ggplot2)
library(scales)
```

#### Presenting how to get the text of a given book:

Get Mark Twain's Tom Sawyer:

```{r}
mark_twain <- gutenberg_works(author == "Twain, Mark", str_detect(title, "The Adventures of Tom Sawyer"))
```

We should look for the id:

```{r}
head(mark_twain[, c("title", "gutenberg_id")])
```

In this case the id for this book is 74.

Find another book:

In this case I choose Agatha Christi's The Secret Adversary:

```{r}
agatha_christie <- gutenberg_works(str_detect(author, "Agatha"))

head(agatha_christie)
```

#### Download both of the book:

```{r, warning=FALSE, message=FALSE}
books <- gutenberg_download(c(74, 1155), meta_fields = "title")
```

#### Use the unnest tokens function to split the data to words:
```{r, , warning=FALSE, message=FALSE}
words <- books %>% unnest_tokens(word, text) %>% anti_join(stop_words)

head(words)
```

Count the words how many times they appear in a book by title and sort them:

```{r}
word_counts <- words %>%
  count(title, word, sort = TRUE)

head(word_counts, 10)
```

#### Plotting:
Which are the most frequent word in The Adventures of Tom Sawyer by Mark Twain?

See the plot below:

```{r}
word_counts %>% 
  filter(n > 50, title == "The Adventures of Tom Sawyer") %>%
  mutate(word = reorder(word,n)) %>%
  ggplot(aes(word, n)) + geom_col() + 
  labs(title = "How many times a given word is mentioed in the The Adventures of Tom Sawyer by Mark Twain", x = "Words", y = "Observations") +
  coord_flip()
```

Which are the most frequent word in The Secret Adversary by Agatha Christie?

See the plot below:

```{r}
word_counts %>% 
  filter(n > 75, title == "The Secret Adversary") %>%
  mutate(word = reorder(word,n)) %>%
  ggplot(aes(word, n)) + geom_col() +
  labs(title = "How many times a given word is mentioed in the The Secret Adversary by Agatha Christie", x = "Words", y = "Observations") +
coord_flip()
```

#### Another type of plot:

We should calculate the frequencies of words by book:

```{r}
word_counts2 <- word_counts %>%
  group_by(title) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(title, proportion)

head(word_counts2, 10)
```

Then, we can inspect the results by piloting the word frequencies together:

```{r, warning=FALSE, message=FALSE}
ggplot(word_counts2, aes(x = word_counts2[,2], y = word_counts2[,3])) + geom_abline(slope =1, linetype=3) + geom_jitter(alpha = 0.1, alpha = 0.1 , color = "blue") + labs(title = paste(c("Word frequincies of:", colnames(word_counts2)[2], "vs",colnames(word_counts2)[3]), collapse = " "), x = colnames(word_counts2)[2], y = colnames(word_counts2)[3]) + geom_text(aes(label = word), color = "blue", alpha = 0.3) + scale_x_log10(labels = percent_format()) + scale_y_log10(labels = percent_format())
```

Brown, miss, sir , round, etc. are frequently used in The Secret Adversary then in The Adventure of Tom Sawyer, while boys, school, water, village are more frequent in Mark Twain's book.
